### 2024-05-19 README.Rmd
Edits

>> Mission Statement  
>> Our organization seeks to level up on all matters related.

## Background: AI roams the World

@@

- Where does it make sense?

@@

- what does a technology do for whom?

@@

@@

```{r plot-simulated-data, fig.cap="Simple Example of a Regression Model"}
ggplot(df,
       aes(x = x,
           y = y)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  theme_minimal()
```

Predict:
```{r data-vs-predictions-comparison, fig.cap="Training data and model output compared"}
df_pred <- data.frame(x = b1 * runif(100, 
                                0, 
                                10))

@@

@@

ChatGPT consumes substantially more than a search...are the results better? [@https://www.brusselstimes.com/1042696/chatgpt-consumes-25-times-more-energy-than-google]

@@

![A search using Duck Duck Go](images/logical-puzzle-web-search.png)

![A conversation with ChatGPT-4](images/logical-puzzle-chat-gpt-4.png)

<!--

<iframe src="https://assemblag.es/@hugo/112450401657084750/embed" width="400" allowfullscreen="allowfullscreen" sandbox="allow-scripts allow-same-origin allow-popups allow-popups-to-escape-sandbox allow-forms"></iframe>

https://assemblag.es/@hugo/112450401657084750 -->

@@

> “The first step in liquidating a people,' said Hubl, 'is to erase its memory. Destroy its books, its culture, its history. Then have somebody write new books, manufacture a new culture, invent a new history. Before long the nation will begin to forget what it is and what it was. The world around it will forget even faster.”
> -― Milan Kundera, The Book of Laughter and Forgetting

>>>>

> Mission Statement: Our organization seeks to level up on all matters related.  
> -- An Organization Run by its Marketing Department

## Background: An AI roams the University

@@

- Where does it make sense? Presumably this is what the Committee on AI will try to answer.

@@

- What does technology X do for whom?

@@

## Not learning

Words go here.

## Learning the wrong stuff

Words go here.

## Deskilling

Words go here.

@@

```{r plot-simulated-data, out.width="50%", fig.cap="Simple Example of a Regression Model"}
ggplot(df,
       aes(x = x,
           y = y)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  theme_minimal()
```

Predict:
```{r data-vs-predictions-comparison, out.width="50%", fig.cap="Training data and model output compared"}
df_pred <- data.frame(x = b1 * runif(100, 
                                0, 
                                10))

@@

Words go here.

@@

ChatGPT consumes substantially more energy than a regular web search...are the results better? [@https://www.brusselstimes.com/1042696/chatgpt-consumes-25-times-more-energy-than-google]

@@

![A search using Duck Duck Go](images/logical-puzzle-web-search.png){width=50%}

![A conversation with ChatGPT-4](images/logical-puzzle-chat-gpt-4.png){width=50%}

https://assemblag.es/@hugo/112450401657084750

<!--
<iframe src="https://assemblag.es/@hugo/112450401657084750/embed" width="400" allowfullscreen="allowfullscreen" sandbox="allow-scripts allow-same-origin allow-popups allow-popups-to-escape-sandbox allow-forms"></iframe>
 -->

@@

>The first step in liquidating a people,' said Hubl, 'is to erase its memory. Destroy its books, its culture, its history. Then have somebody write new books, manufacture a new culture, invent a new history. Before long the nation will begin to forget what it is and what it was. The world around it will forget even faster.  
>-― Milan Kundera, The Book of Laughter and Forgetting
